Solving the Poisson-equation in one dimension \\ \hrulefill\small{ FYS3150: Computational Physics }\hrulefill

### 2016-09-15 Project1/article/article.tex
Some additions to LU

The LU decompositon method is a method where the matrix $A$ in
equation \ref{eq:matrix} ($A\vb{v}=\vb{f}$) can be rewritten as a product of two matrices
$L$ and $U$, where $L$ is lower triangular and and $U$ is upper
triangular. This method only works for non-singular, invertible
matrices, which the matrix $A$ certainly is.

>>>>

The LU decomposition method is a method where the matrix $A$ in
equation \ref{eq:matrix} ($A\vb{v}=\vb{f}$) can be rewritten as a product of two matrices
$L$ and $U$, where $L$ is lower triangular and and $U$ is upper
triangular. This method only works for non-singular, invertible
matrices, which the matrix $A$ certainly is. 
\begin{equation}
A = LU =
\begin{bmatrix}
1 & 0 & 0 & \dots & 0 & 0 \\
l_{21} & 1 & 0 & \dots & 0 & 0 \\
l_{31} & l_{32} & 1 & \dots & 0 & 0 \\
  &\vdots & & \ddots & \vdots  & \\
l_{n-11} & l_{n-12} & l_{n-13} & \dots & 1 & 0 \\  
l_{n1} & l_{n2} & l_{n3} & \dots & l_{nn-1} & 1
\end{bmatrix}
\begin{bmatrix}
u_{11} & u_{12} & u_{13} & \dots & u_{1n-1} & u_{1n} \\
0 & u_{22} & u_{23} & \dots & u_{2n-1} & u_{2n} \\
0 & 0 & u_{33} & \dots & u_{3n-1} & u_{3n} \\
  &\vdots & & \ddots & \vdots  & \\
0 & 0 & 0 & \dots & u_{n-1n-1} & u_{n-1n} \\  
0 & 0 & 0 & \dots & 0 & u_{nn}
\end{bmatrix}
\end{equation}

The previous equation can be solved in two steps
\begin{equation}
L\vb{w}=\vb{f}, \quad U\vb{v}=\vb{w}
\end{equation}
